Supercritical fluid extraction of essential oil from chamomile flowers: modelling, and parameter estimation

### 2024-04-15 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Experiments.tex
12.04
15.04

	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to calibrate the model based on the experimental the dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile flowers. The experiments were performed by \citet{Povh2001} and \citet{Rahimi2011}.	The experiments were conducted using an a semi-batch extractor with diameter of 3.96 [cm] and length of 16.55 [cm]. Twelve experiments were performed under different operating conditions: $30-40^\circ C$, $100 - 200$ [bar], and $0.05 - 0.24$ [kg/h]. The amount of solid material used for extraction was $75$ [g], which was sufficient to fill the whole vessel. The bulk density of the bed was computed based on the feed's mass and the extractor's volume. The total porosity of the bed, including the particles, was determined using the following calculation: $\epsilon=1-\frac{d_a}{d_r} = 1-\frac{370}{1364} = 0.73$.

>>>>

	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to calibrate the model based on the experimental the dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile flowers. The experiments were performed by \citet{Povh2001} and \citet{Rahimi2011}. The experiments were conducted using a semi-batch extractor with a diameter of 3.96 [cm] and a length of 16.55 [cm]. Twelve experiments were performed under different operating conditions: $30-40^\circ C$, $100 - 200$ [bar], and $0.05 - 0.24$ [kg/h]. The amount of solid material used for extraction was $75$ [g], which was sufficient to fill the whole vessel. The bulk density of the bed was computed based on the feed's mass and the extractor's volume. The total porosity of the bed, including the particles, was determined using the following calculation: $\epsilon=1-\frac{d_a}{d_r} = 1-\frac{370}{1364} = 0.73$. It is assumed that the total amount of the extract is equal 3 [g], defined as to the biggest obtained yield after rounding up.

### 2024-04-15 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Model.tex
15.04

		On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$. $c_p^*$ is determined by an equilibrium relationship with $c_f$ and the extraction rate given by Equation \ref{Model_kinetic_basic}

>>>>

		On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$.Concentration $c_p^*$ is determined by an equilibrium relationship with $c_f$ and the extraction rate given by Equation \ref{Model_kinetic_basic}
